Stellar Radiation is Critical for Regulating Star Formation and Driving Outflows in Low Mass Dwarf Galaxies

### 2019-03-19 thesis/chapters/ch_chapter1.tex
adding reference

We make the common ansatz that star formation occurs by converting gas into stars in a free fall time $\tau_{\rm ff}$ with a star formation efficiency, $\epsilon_{\rm f} \simeq 0.02$. At high resolution, the choice of $\epsilon_{\rm f}$ should be irrelevant \citep{Orr2018, FIRE2}, as star formation is ultimately self-regulated by feedback.

>>>>

We make the common ansatz that star formation occurs by converting gas into stars in a free fall time $\tau_{\rm ff}$ with a star formation efficiency, $\epsilon_{\rm f} \simeq 0.02$ \citep{KrumholzTan2007}. At high resolution, the choice of $\epsilon_{\rm f}$ should be irrelevant \citep{Orr2018, FIRE2}, as star formation is ultimately self-regulated by feedback.
